{\bf I JUST COPIED THIS IN FROM ANOTHER GRANT; FIX ME}

\bigskip \noindent{\sc PI Salaries:} 

We include 3 months salary per year for PI Becker. Becker is on the
Research Faculty at UW, meaning his salary must be accumulated through
grants such as this one.  Benefits are calculated at the rate of
$27.2\%$.  We budget for a $2\%$ annual increase in these salaries.

\bigskip \noindent{\sc Other Salaries:} 

Two graduate students will be funded for 3 academic quarters per year.
Benefits are calculated at the rate of $16.1\%$.  We budget for a
$2\%$ annual increase in these salaries.  We budget for a $\$2,000$
per--summer stipend for the undergraduate student to participate in
the NASA Space Grant's Summer Undergraduate Research Program (SURP).
Participating faculty are responsible for providing funding for half
of their SURP student's stipend ($\$4,000$).

\bigskip \noindent{\sc Tuition Costs:} 

We include tuition fees for the two graduate students at the rate of
$\$4,294$ per quarter, for 3 academic quarters per student per year.
We budget for a $10\%$ annnual increase in these fees.

\bigskip \noindent{\sc Equipment:} 

We will need a database machine that supports, at a minimum,
approximatly 3 TB of MySQL database to hold the Level 1b and Level 3
products.  This machine will be used to stage the bulk data from IPAC,
ingest the data into MySQL, build indices and views on the tables,
cluster the data from SDSS and WISE using the {\tt OPTICS} algorithm,
search for periods within the Level 1b clusters, and store the
intermediate data products.  In total this calls for 5 TB of RAIDed
storage space, and multi--core processing capabilities.  We request a
medium--sized memory configuration of 128 GB, as memory limitations
will impact the granularity of the sky tracts that can be fed into
{\tt OPTICS}.  There are additional constraints on the machine that
have to do with the current UW compute infrastructure, that
essentially require that we purchase a Dell Poweredge rack--based
server.  We have a quote from Dell for a PowerEdge R715 database
server, including two 12--core processors, 128 GB of memory, and 6 TB
of RAIDed disk for $\$11$k.  We assume that by the time the machine is
needed this price will be under $\$10$k.  We will purchase whatever
equivalent is available in 2013 for the cost of $\$10$k.

\bigskip \noindent{\sc Travel:} 

We budget for 2 domestic trips per year for collaboration and
conferences, at the rate of $\$1,821$ per trip (to cover travel to and
4 days lodging and per diem at reference destination Washington, DC).
This will be shared by the PI, graduate students, and potentially the
undergraduate student. We budget for a $2\%$ annual increase in these
costs.

\pagebreak

\bigskip \noindent{\sc Publication Charges:} 

Publication costs are budgeted at the electronic publishing charge
of \$110/page, for 30 pages/year.

\bigskip \noindent{\sc Computing Fees:} 

Computer support fees are budgeted at the nominal rate of \$67 per
person per month by the Physics and Astronomy Computing Services group
(PACS) at UW.  We budget for a $3\%$ annual increase in these costs.

\bigskip \noindent{\sc Indirect Costs:} 

Indirect costs are based on the MTDC rate of $54.5\%$ per the
negotiated agreement with DHHS dated 9/22/2011.

\bigskip \noindent{\sc Personnel and Work Effort:}

PI Becker will work on this project at $25\%$ effort for the duration
of the project.  Early work will include the technical implementation
of the algorithms on the compute infrastructure, optimizing database
queries, and assisting the graduate students on software development.
Subsequent work will include data mining of the time--domain database,
in particular on the analysis of the variable star sample and
follow--up observations.

Co--I Ivezi\'{c} will assist as--needed in the guiding the science
objectives of the multi--band analysis, including the extragalactic
science and the use of the {\tt Dusty} software suite.

Graduate student A will work primarily with the {\bf L3} data
products, the multi--wavelength component of the proposal.

Graduate student B will work primarily with the {\bf L1b} data
products, the multi--epoch component of the proposal.

The undergraduate students will be educated in the basics of computer
programming in the early portions of the proposal by PI Becker.  As
their skills develop they will assist in the analysis tasks being
undertaken by graduate students A and B.

\bigskip \noindent{\sc Facilities and Equipment:}

The database machine needed for this proposal is described in detail
on the preceding page.  Basic compute resources are provided to all
graduate students by the Department of Astronomy, and the
Investigators have their own desktop machines.  The only other
resource in--scope for this project is the 560--node {\tt Minerva}
compute cluster at UW.  This will be used for the low--memory, highly
parallelizable portions of the data analysis, in particular the
per--band summary statistics of the {\bf L1b} lightcurves.

