\def\etal{{\it et al.\thinspace}}
\documentclass[12pt]{article}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.0in}


\begin{document}

\newpage
\begin{center}
\LARGE
{Dr. Rory Kevin Barnes\\}
\normalsize
\end{center}

%ADDRESS SECTION
\begin{tabbing}
xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxx \= xxxxxxxxxxx \=    \kill
{\bf Address} \> Astronomy Dept. \> {\bf Phone} \>
(206)543-8979\\
                \> University of Washington \> {\bf FAX} \> (206)685-0403\\
                \> Box 351580 \> {\bf E-mail} \> rory@astro.washington.edu\\
                \> Seattle, WA, USA \> {\bf Citizenship} \>USA
\end{tabbing}

\noindent
{\bf EMPLOYMENT} \\
\textbf{2011 -- } Research Staff, Astronomy Dept. \& Astrobiology Program, U. of Washington\\
\textbf{2009 -- 2011} VPL/IGERT Postdoctoral Research Associate to 
Victoria Meadows, Astronomy Dept., U. of Washington\\
\textbf{2004 -- 2008} Postdoctoral Research Associate to Richard 
Greenberg, Lunar and Planetary Laboratory, U. of Arizona.\\
\\
\noindent {\bf EDUCATION} \\
Ph.D. Astronomy, University of Washington, 2004\\
\indent Dissertation: Dynamics of the Initial Planetesimal Disk (Adviser: 
Thomas Quinn)\\
M.S. Astronomy, University of Washington, 1999\\
B.S. Astronomy, University of Arizona, 1998 \\
B.S. Physics, University of Arizona, 1998 \\
\\
\textbf{HONORS AND AWARDS}\\
\textbf{2002-2004} NASA GSRP Fellowship\\
\textbf{2009} NASA Group Achievement Award (for my contribution to the SIM Double Blind study)\\\\
\noindent
{\bf SELECTED RELEVANT PUBLICATIONS} \\
\underline{A. Book}\\
{\it Formation and Evolution of Exoplanets}. 2010. \textbf{R. Barnes} (Ed.),
Wiley-VCH. Berlin\\\\
\underline{B. Refereed Publications}\\
\textbf{Barnes, R.} \etal 2013. Tidal Venuses: Triggering a Climate Catastrophe via Tidal Heating. {\it Astrobiology}, 13, 
\vspace{0.1cm}
279--291.\\
Kundurthy, P., \textbf{Barnes, R.} \etal 2013. APOSTLE: Longterm Transit Monitoring and Stability Analysis of XO-2b. {\it Astrophys. J.}, 
\vspace{0.1cm}
submitted.\\
\textbf{Barnes, R.} \etal 2011. Origin and Dynamics of the Mutually Inclined Orbits of $\upsilon$ Andromedae c and d. {\it Astrophys. J.}, 
\vspace{0.1cm}
726, 71.\\
Jackson, B., Miller, N., \textbf{Barnes, R.}, \etal 2010. The Roles of Tidal Evolution and Evaporative Mass Loss in the Origin of CoRoT-7 b. {\it Mon. Not. Roy. Astron. Soc.}, 
\vspace{0.1cm}
407, 910-922.\\
\textbf{Barnes, R.} \etal 2008. Tides and the Evolution of Planetary Habitability. {\it Astrobiology}, 8,
\vspace{0.1cm}
557-568.\\
\textbf{Barnes, R.}, \& Greenberg, R., 2006. Behavior of Apsidal Motion in
Planetary Systems. 
\vspace{0.1cm}
\textit{Astrophys. J.}, 652, 53-56.\\
\textbf{Barnes, R.}, \& Greenberg, R. 2006. Extrasolar Planetary Systems
  Near a Secular Separatrix. {\it Astrophys. J.} 638, 478 -- 487. \\

\end{document}
